Weather Data Integration and Assimilation System\\

### 2020-02-09 thesis.tex
Fix: Reference numbers should ideally not be listed with Figure names.
Updated the abstract

%To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These \acrshort{nwm} 
\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such %diverse 
multimodal data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to %accommodate critical situations 
forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. Providing public to access weather data is also useful to enable many third-party applications and research. For example, logistic companies could use those data within their models to plan and schedule deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.

%While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further Delft-FEWS is free to use, it is not open source. Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements. Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.

\dbc{Add a set of sentences covering the why a new solution is needed, what sort of a solution we propose, how does the proposed solution work, why it's unique, and its performance. Abstract should not exceed 300 words. Typically background given in above para should not be more than 1/3 of abstract.}

@@

\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
\dbc{Sort these. Add 2 more CS related terms. Remove WDIAS.}
}
\restoregeometry
\normalsize

@@

\addcontentsline{toc}{chapter}{List of Figures}
\dbc{Reference numbers should ideally not be listed with Figure names.}
\listoffigures

>>>>

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to using such multimodal data into respective \acrshort{nwm}, it is necessary to transcode into a format that can be ingested by the \acrshort{nwm} modal. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. Later such weather data needs to be accessed by many third-party applications and research in order to make use of them. Thus the system should provide easy protocol to integrate with external systems, and should be capable of handling the workload. For example, logistic companies could use those data within their models to plan and schedule deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.

Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. \acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture.

It provides a modular approach to integration of data from different sources and export into different formats, and inbuilt extension module system allow users to add new features. Since each module follows the stateless and failover microservice integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box. The proposed solution is independent of the platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it. And the auto scaling feature allows users to run \acrshort{wdias} from 1 CPU node to nodes with a few hundred CPUs. Unlike most existing systems \acrshort{wdias} does not require a shutdown in order to update the system configuration, and it allows to add new features on the fly with rollover capabilities.

@@

\textbf{Keywords:} Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
}
\restoregeometry
\normalsize

@@

\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
